%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Trey Hunner (http://www.treyhunner.com/)
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document 
\usepackage{sectsty}
\usepackage{fancyhdr}
\usepackage{lastpage}
\pagestyle{fancy} 
\lhead{}  
\chead{} 
\cfoot{- \thepage\ of \pageref{LastPage} -}
\rfoot{Curriculum Vitae}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\usepackage{enumitem}
\usepackage[pdftex]{color,hyperref}
\hypersetup{colorlinks,breaklinks,
            linkcolor=blue,urlcolor=blue,
            anchorcolor=blue,citecolor=blue}

\newcommand\doilink[1]{\href{http://dx.doi.org/#1}{#1}}
\newcommand\doi[1]{doi:\doilink{#1}}

% \makeatletter
% \newlength{\bibhang}
% \setlength{\bibhang}{1em} %1em}
% \newlength{\bibsep}
%  {\@listi \global\bibsep\itemsep \global\advance\bibsep by\parsep}
% \newenvironment{bibsection}%
%         {\begin{enumerate}{}{%
% %        {\begin{list}{}{%
%        % \setlength{\leftmargin}{\bibhang}%
%        % % \setlength{\itemindent}{-\leftmargin}%
%        % \setlength{\itemsep}{\bibsep}%
%        % \setlength{\parsep}{\z@}%
%        %  \setlength{\partopsep}{0pt}%
%         % \setlength{\topsep}{0pt}
%         }}
%         {\end{enumerate}}
% %        {\end{list}\vspace{-.6\baselineskip}}
% \makeatother

% \renewenvironment{itemize}{
%   \begin{list}{}{
%     \setlength{\leftmargin}{1.5em}
%     \setlength{\itemsep}{0.2em}
%     \setlength{\parskip}{0pt}
%     \setlength{\parsep}{0.2em}
%   }
% }{
%   \end{list}
% }
% \setlist[enumerate]{itemsep=0.2em}


% For \url{SOME_URL}, links SOME_URL to the url SOME_URL
\providecommand*\url[1]{\href{#1}{#1}}
% Same as above, but pretty-prints SOME_URL in teletype fixed-width font
\renewcommand*\url[1]{\href{#1}{\texttt{#1}}}

% For \email{ADDRESS}, links ADDRESS to the url mailto:ADDRESS
\providecommand*\email[1]{\href{mailto:#1}{#1}}

\name{Huanle Xu} % Your name
% \email{Email: xh112@ie.cuhk.edu.hk}  % Your address
% \address{SHB 802, CUHK, Shatin, N.T., Hong Kong}
%\address{The Chinese University of Hong Kong} % Your secondary addess (optional)}
% \address{Homepage: http://home.ie.cuhk.edu.hk/~xh112}

\begin{document}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------
\vspace{-3em}

\begin{rSection}{Contact}
\begin{minipage}[t]{0.495\textwidth}
  Postdoc Fellow\\
  Department of Information Engineering \\
  The Chinese University of Hong Kong
  
\end{minipage}
\begin{minipage}[t]{0.495\textwidth}
  Phone: (+852)95671589 \\
  Email: \email{xhlcuhk@gmail.com} \\
  % Homepage: \href{https://xuhappy.github.io/home/}{http://home.ie.cuhk.edu.hk/$\sim$xh112}
  % Homepage: \href{http://home.ie.cuhk.edu.hk/~hlxu/}{http://home.ie.cuhk.edu.hk/~hlxu/} \\
  Postal Address: SHB 802, CUHK, Shatin, N.T., Hong Kong 
\end{minipage}
\end{rSection}



\begin{rSection}{Education}
\begin{rSubsection}{The Chinese University of Hong Kong}{Aug. 2012 - Aug. 2016 } {}{}
\item[] Ph.D. in Information Engineering \\
Dissertation Advisor: Prof. \href{http://personal.ie.cuhk.edu.hk/~wclau/}
                   {Wing Cheong Lau}, 
\end{rSubsection} 

% \end{rSubsection}
\begin{rSubsection}{Shanghai Jiao Tong University} {Sep. 2008 - Jun. 2012}{}{}
\item[]  
BSc.(Eng). in Information Engineering \\
Ranking: Top 8\%
\end{rSubsection}

\end{rSection}

\begin{rSection}{Research Experience}
% \begin{rSubsection}{The Chinese University of Hong Kong}{Sep. 2016 - Feb. 2017}{Postdoc Fellow in Information Engineering Department}{Advisor: Prof. \href{http://personal.ie.cuhk.edu.hk/~wclau/}
%                    {Wing Cheong Lau}}
% \item[]
% \end{rSubsection}
% \vspace{-2.5em}
% \begin{itemize}
% \item  Design online learning algorithms to mitigate the straggler problem in big data processing clusters.
% \end{itemize}
\begin{rSubsection}{The University of Texas at Austin}{Sep. 2015 - Feb. 2016}{Visiting Scholar in ECE Department}{Advisor: Prof. \href{http://users.ece.utexas.edu/~gustavo/}
                   {Gustavo de Veciana}}
\item[]
\end{rSubsection}
\vspace{-2.5em}
\begin{itemize}
\item  Design online resource allocation policies in big data processing clusters, combining redundant execution with opportunistic checkpointing so as to minimize the overall job delays.
\end{itemize}
\end{rSection}
%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Research Interests}
\begin{itemize}
\setlength{\leftmargin}{0em}
    \setlength{\itemsep}{0.2em}
    \setlength{\parskip}{0pt}
\item Design, Implementation, Performance Optimization in Big Data Processing Systems
\item Online Learning with Bandit Problems
\item Algorithm and Protocol Design in Decentralized Social Networks
\item Graph Algorithm Design under Parallel Processing Frameworks 
\item Distributed Storage Codes Design
% \end{rSubsection}
\end{itemize}
%------------------------------------------------



%------------------------------------------------
\end{rSection}


\begin{rSection}{Recent Research Projects}
\begin{rSubsection}{Online Algorithm Design in the Bandit Setting}{}{}{}
\item[]
% \end{itemize}
\end{rSubsection}
\vspace{-2.5em}
\begin{itemize}
\setlength{\leftmargin}{0em}
    \setlength{\itemsep}{0.2em}
    \setlength{\parskip}{0pt}
\item Design online learning algorithms to mitigate machine service variability from a bandit perspective. 
\item Design Task Assignment policy in Crowdsourcing Environment using linear contextual bandits. 
\end{itemize}

\begin{rSubsection}{Speculative Execution Mechanism in Big Data Processing Systems}{}{}{}
\item[]
% \end{itemize}
\end{rSubsection}
\vspace{-2.5em}
\begin{itemize}
\setlength{\leftmargin}{0em}
    \setlength{\itemsep}{0.2em}
    \setlength{\parskip}{0pt}
\item Design and implement resource allocation modules under MapReduce/ Hadoop YARN. 
\item Plug in speculative execution schemes to enhance fault tolerance computing and reduce job response time. 
\end{itemize}

\begin{rSubsection}{Resource Allocation Algorithms for Large-Scale Clusters with Performance Guarantees}{}{}{}
\item[]
\end{rSubsection}
\vspace{-2.5em}
\begin{itemize}
\setlength{\leftmargin}{0em}
    \setlength{\itemsep}{0.2em}
    \setlength{\parskip}{0pt}
\item Combine Job scheduling and speculative execution to maximize system utility, which is a combination of job response time and computation cost.
\item Design task cloning algorithms with competitive performance bounds to reduce job response time.
\end{itemize}

\begin{rSubsection}{Protocol Design and Performance Analysis for Decentralized Social Networks}{}{}{}
\item[]
\end{rSubsection}
\vspace{-2.5em}
\begin{itemize}
\setlength{\leftmargin}{0em}
    \setlength{\itemsep}{0.2em}
    \setlength{\parskip}{0pt}
\item Design a message dissemination protocol in Decentralized Social Networks to maximize system utility from an optimization perspective.
\end{itemize}
\end{rSection}
%----------------------------------------------------------------------------------------
%	TECHNICAL STRENGTHS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Publications}
\begin{enumerate}
    \setlength{\leftmargin}{0em}
    \setlength{\itemsep}{0.2em}
    \setlength{\parskip}{0pt}
    \item \textbf{Huanle Xu}, Gustavo de Veciana, Wing Cheong Lau and Kunxiao Zhou, ``Online Job Scheduling with Redundancy and Opportunistic Checkpointing: A Speedup-Function-Based Analysis'', in IEEE Transactions on Parallel and Distributed Systems ({IEEE TPDS}), accepted for publication, Sep 2018. 
    \item \textbf{Huanle Xu}, Wing Cheong Lau, Zhibo Yang, Gustavo de Veciana and Hanxu Hou, ``Mitigating Service Variability in MapReduce Clusters via Task Cloning: A Competitive Analysis'', in IEEE Transactions on Parallel and Distributed Systems ({IEEE TPDS}), Vol.18, Issue 10, Oct 2017. 
    \item {\bf Huanle Xu} and Wing Cheong Lau, ``Optimization for Speculative Execution in Big Data Processing Clusters'', in IEEE Transactions on Parallel and Distributed Systems ({IEEE TPDS}), Vol.28, Issue 2, Feb 2017. 
    \item Zhibo Yang, {\bf Huanle Xu*}, Jianyuan Deng, Chen Change Loy and Wing Cheong Lau, ``Robust and Fast Decoding of High-Capacity Color QR Codes for Mobile Applications'', in IEEE Transactions on Image Processing, accepted for Publication, July 2018.
    \item \textbf{Huanle Xu}, Gustavo de Veciana and  Wing Cheong Lau, ``Addressing Job Processing Variability Through Redundant Execution and Opportunistic Checkpointing:  A Competitive Analysis'', in {IEEE Infocom} 2017. 
    \item \textbf{Huanle Xu} and Wing Cheong Lau, ``Task-Cloning Algorithms in a MapReduce Cluster with Competitive Performance Bounds", in {IEEE ICDCS} 2015.
    \item \textbf{Huanle Xu} and Wing Cheong Lau, ``Optimization for Speculative Execution in a MapReduce-like Cluster'', in {IEEE Infocom} 2015.
    \item \textbf{Huanle Xu}, Pili Hu, Wing Cheong Lau, Qiming Zhang and Yang Wu, ``DPCP: A Protocol for Optimal Pull Coordination in Decentralized Social Networks'', in {IEEE Infocom} 2015.
    \item \textbf{Huanle Xu}, Ronghai Yang, Zhibo Yang and Wing Cheong Lau, ``Solving Large Graph Problems in MapReduce-Like Frameworks via Optimized Parameter Configuration'', in the 15th International Conference on Algorithms and Architectures for Parallel Processing (ICA3PP), 2015.
        %To appear \emph{Alcoholism: Clinical and Experimental Research}, 2012.
    \item \textbf{Huanle Xu} and Wing Cheong Lau, ``Speculative Execution for a Single Job in a MapReduce-like System'', in IEEE International Conference on Cloud Computing {(IEEE Cloud)}, 2014.
    \item \textbf{Huanle Xu} and Wing Cheong Lau, ``Resource Optimization for Speculative Execution in a MapReduce Cluster'' (PhD Forum), in {IEEE ICNP} 2013.
     \item Ruohan Gao, \textbf{Huanle Xu}, Pili Hu and Wing Cheong Lau, ``Accelerating Graph Mining Algorithms via Uniform Random Edge Sampling'', in {IEEE ICC} 2016. 
     \item Kenneth W. Shum, Hanxu Hou, Minghua Chen, \textbf{Huanle Xu} and Hui Li, ``BASIC Codes: Low-Complexity Regenerating Codes for Distributed Storage Systems'', in IEEE International Symposium on Information Theory (IEEE ISIT), 2014.
\end{enumerate}
% \end{bibsection}


% \newcounter{9}
% \begin{list}{}
%   {\usecounter{9}
%   \setlength{\rightmargin}{\leftmargin}}
% \item This is the first item
% \item And this is the second item
% \end{list}

\end{rSection}


% \begin{rSection}{Working Papers}
% \begin{enumerate}
%  \setcounter{enumi}{11}
%     \setlength{\leftmargin}{0em}
%     \setlength{\itemsep}{0.2em}
%     \setlength{\parskip}{0pt}
%     \item \textbf{Huanle Xu}, Yang Liu and Wing Cheong Lau, ``Online Job Scheduling with Resource Packing on a Cluster of Heterogeneous Servers'', under submission. 
%     \item Yang Liu, \textbf{Huanle Xu} and Wing Cheong Lau, ``Cost Effective Resource allocation for Approximation Jobs: A Bandit Approach'', under submission. 
%     % \item Zhibo Yang, \textbf{Huanle Xu}, Keda Fu and Yong Xia, ``Similar Handwritten Chinese Character Discrimination by Weakly Supervised Learning''.
% \end{enumerate}
% % \end{bibsection}
% \end{rSection}

\begin{rSection}{Honors/ Awards}
\begin{itemize}
    \setlength{\itemsep}{0.2em}
    \setlength{\parskip}{0pt}
\item Reaching Out Award of CUHK \hfill May 2016
\item Overseas Research Attachment Programme Award of CUHK \hfill Oct 2015 
\item Student Travel Grant for MLSS Beijing \hfill June 2014
\item Student Travel Grant for ICNP \hfill Oct 2013
\item 1st Prize in National Mathematical Contest in Modeling \hfill Nov 2011
\item 3rd Prize in National  Mathematical Tournament in Modeling (23/1772) \hfill May 2011
\end{itemize}
\end{rSection}


% \begin{rSection}{Skills}
% \begin{itemize}
%     \setlength{\itemsep}{0.2em}
%     \setlength{\parskip}{0pt}
% \item {Programming Language:}{\quad C++, Java}
% \item {Simulation Program:}{\quad NS2, Matlab}
% \end{itemize}
% \end{rSection}

\begin{rSection}{Graduate Coursework}
\begin{tabular}{llll}
Information Theory & & &\qquad \qquad  \qquad \qquad  \qquad{Foundations of Optimization}  \\
 {Random Process}  & & & \qquad \qquad \qquad \qquad  \qquad {Randomness and Computation}  \\
 {Big Data Analytics} & & & \qquad \qquad \qquad \qquad  \qquad {Machine Learning} \\
{Optimization in Networks and Systems} 
\end{tabular}
\end{rSection}


\begin{rSection}{Teaching Assistant Experiences}
\begin{tabular}{llll}
Signal and Systems & & & \quad Networking Protocols and Systems\\
Principles of Communication Systems & & & \quad Telecommunication Switching and Network Systems \\
Advanced Topics in Cloud Computing  & & & \quad Big Data Systems and Information Processing \\
Operation and Optimization Methods & & &
\end{tabular}
\end{rSection}

\begin{rSection}{Skills}
\begin{itemize}
 \setlength{\itemsep}{0.2em}
    \setlength{\parskip}{0pt}
\item C/C++, Matlab, Java, Python
\item Latex, Git
% \cvline{SEEM 5520}{Foundations of Optimization \ \ $A$}
% \cvline{IERG 5300}{Random Process \ \ $A$}
% \cvline{CSCI 5450}{Randomness and Computation \ \ $A$}
% \cvline{CSCI 5510}{Big Data Analytics \ \ $A^-$}
% \cvline{IERG 6200}{X-Optimization In Networks And Systems \ \ $A$}
% \cvline{CSCI 5030}{Machine Learning  \ \ $A$}
\end{itemize}
\end{rSection}

\begin{rSection}{Professional Services}
\begin{itemize}
 \setlength{\itemsep}{0.2em}
    \setlength{\parskip}{0pt}
\item Reviewer for IEEE Infocom, IEEE ICC, IEEE Globecom 
\item Student Volunteer for IEEE Infocom 2015 
\item Student Volunteer for ACM Sigcomm 2013
% \cvline{SEEM 5520}{Foundations of Optimization \ \ $A$}
% \cvline{IERG 5300}{Random Process \ \ $A$}
% \cvline{CSCI 5450}{Randomness and Computation \ \ $A$}
% \cvline{CSCI 5510}{Big Data Analytics \ \ $A^-$}
% \cvline{IERG 6200}{X-Optimization In Networks And Systems \ \ $A$}
% \cvline{CSCI 5030}{Machine Learning  \ \ $A$}
\end{itemize}
\end{rSection}


\begin{rSection}{References}
\item[] Prof. Wing Cheong Lau (Dissertation Advisor)\\
Director of Mobile Technologies Center\\
Dept. of Information Engineering\\
The Chinese University of Hong Kong\\
Shatin, N.T., Hong Kong \\
Email: \email{wclau@ie.cuhk.edu.hk} \\
Tel: +852 3943-8356 \\

\item[] Prof. Gustavo de Veciana (IEEE Fellow)\\
Dept. of Electrical and Computer Engineering\\
The University of Texas at Austin\\
1 University Station C0803\\
Austin, TX 78712-0240 \\
Email: \email{gustavo@ece.utexas.edu} \\
Tel: +1 512-471-1573 \\


\item[] Prof. Dah Ming Chiu (IEEE Fellow)\\
Dept. Information Engineering\\
The Chinese University of Hong Kong\\
Shatin, N.T., Hong Kong\\
Email: \email{dmchiu@ie.cuhk.edu.hk}\\
Tel: +852 3943-8357
\end{rSection}
%----------------------------------------------------------------------------------------
%	EXAMPLE SECTION
%----------------------------------------------------------------------------------------

%\begin{rSection}{Section Name}

%Section content\ldots

%\end{rSection}

%----------------------------------------------------------------------------------------

\end{document}
